
\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\projectsubheading}[2]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
\textbf{\large Zhan Haoxun}  & 135.7032.2748 (cell)\\
                             & programmer.zhx@gmail.com\\
                             & http://haoxun.org\\
\end{tabular*}
\\

\vspace{0.1in}


\resheading{Education}
\begin{itemize}
\item
  \ressubheading{South China University of Technology}{Guangzhou, China}{Undergraduate of Software Engineering}{Sep. 2011 - Jul. 2015}
\end{itemize}


\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Tencent, Inc.}{Shenzhen, China}{Internship of Technology and Engineering Group(TEG)}{Jul. 2014 - Sep. 2014}
    \begin{itemize}
      \resitem{Worked on an internship project with the theme of figuring out the hot topics of Weibo.
      The project consists of five components: data landing, spam filtering, topic clustering, sub-topic mining and web presenting.
      I was responsible for two components, data landing and sub-topic mining.
      As a technical leader of the team, I've maked suggestion and decision on the design of the project,
      and things such as language style guide, toolchain, autotool and test framework.}
    \end{itemize}

\end{itemize}


\resheading{Skills}
\begin{description}

\item[Python:] Intermediate level, two years experience.
Carefully studied the official \textit{language reference}, several \textit{PEPs} and books such as \textit{Python Cookbook}.
Familiar with the standard library, coding convention and development tools.
Experience developing several personal projects(\textit{e.g.}, \textit{GeekCMS}, \textit{GoogleTranslateAPI} and \textit{MyGoogleDict}) in python.

\item[C++:] Intermediate level, one year experience. Carefully studied \emph{C++ Primer 5ed}, \emph{Google C++ Style Guide}
and some materials in \textit{cppreference.com}.
Familiar with features of \textit{C++11}, the standard library and object-oriented paradigm of C++.
Experience developing projects(\textit{intern project} and \textit{in-school project}) in collaboration.

\item[Operating Systems:] Long-term user of \textit{OS X} and \textit{Ubuntu}. Experience with command-line interface and shell.

\item[Others:] Experience in \textit{Vim} and {Git}.

\end{description}


\resheading{Personal Projects}
\begin{itemize}
\item
  \projectsubheading{GeekCMS}{Nov. 2013 - Apr. 2014}
    \begin{itemize}
      \resitem{A lightweight framework for static site development.}
    \end{itemize}

\item
  \projectsubheading{GoogleTranslateAPI}{Jan. 2014 - Feb. 2014}
    \begin{itemize}
      \resitem{A Python API of google translation service by simulating browser interaction of \textit{translate.google.com}.}
    \end{itemize}

\item
  \projectsubheading{MyGoogleDict}{Jan. 2014 - Feb. 2014}
    \begin{itemize}
      \resitem{A command-line interface of google translation service, with the features of multi-language support, TTS and history recording.}
    \end{itemize}

\end{itemize}


\resheading{Team Projects}
\begin{itemize}
\item
  \projectsubheading{ShareDoc}{Sep. 2013 - Dec. 2013}
    \begin{itemize}
      \resitem{A file sharing site based on \textit{Django} framework.}
    \end{itemize}

\item
  \projectsubheading{Q-Chatbot}{Jun. 2014 - Jul. 2014}
    \begin{itemize}
      \resitem{A chatbot project based on \textit{Qrobot} hardware.}
    \end{itemize}

\item
  \projectsubheading{Hot topic mining on Weibo}{Jul. 2014 - Sep. 2014}
    \begin{itemize}
      \resitem{An Internship project with the theme realted to data mining.}
    \end{itemize}

\end{itemize}


\end{document}
